### 2017-04-14 paper/oopsla17-submission/overview.tex
some notes

@@

@@

\mypara{Contextual Features: Error Slices}
%
Our contextual features include the
syntactic class of the neighboring
expressions and their inferred types
(when available).
%
However, we have found that
the most important contextual
signal is whether or not the
expression occurs in a
\emph{minimal type error slice}
\citep{Tip2001-qp,Haack2003-vc}
which includes the smallest
subset of all expressions
that are necessary for the
error to manifest.
%
We propose to use type error slices
to communicate to the classifier
which expressions could
\emph{potentially} be blamed --- a
change to an expression outside of
the minimal slice cannot possibly
fix the type error.
%
We empirically demonstrate that
the type error slice is so
important (\autoref{sec:feature-utility})
that it is actually beneficial to
automatically discard expressions
that are not part of the slice,
rather than letting the classifier
learn to do so.
%
Indeed, this domain-specific
insight is crucial for learning
classifiers that significantly
outperform the state-of-the-art.

>>>>

\ES{FIXME: this feels a bit redundant with CHALLENGE 1. the main thing i
  get is that we use student fixes to extract AST-diffs, which is
  already said in CHALLENGE 1}

@@

\ES{FIXME: this feels a bit redundant with CHALLENGE 2. the main things
  i get here are that we use sets of feature vectors, and that we can
  concatenate vectors to add context. but this is all said in CHALLENGE
  2 already.}

@@

\mypara{Contextual Features: Error Slices}
%
Our contextual features include the
syntactic class of the neighboring
expressions and their inferred types
(when available).
%
However, we have found that
the most important contextual
signal is whether or not the
expression occurs in a
\emph{minimal type error slice}
\citep{Tip2001-qp,Haack2003-vc}
which includes the smallest
subset of all expressions
that are necessary for the
error to manifest.
%
\ES{FIXME: this is a bit imprecise. we compute \textbf{a} minimal slice (ie if
  you remove any more terms the error disappears) but not \textbf{the} minimal
  slice. there may be other slices that are smaller, but computing all
  slices is exponential, so we don’t want to do that..}
%
We propose to use type error slices
to communicate to the classifier
which expressions could
\emph{potentially} be blamed --- a
change to an expression outside of
the minimal slice cannot possibly
fix the type error.
%
We empirically demonstrate that
the type error slice is so
important (\autoref{sec:feature-utility})
that it is actually beneficial to
automatically discard expressions
that are not part of the slice,
rather than letting the classifier
learn to do so.
%
Indeed, this domain-specific
insight is crucial for learning
classifiers that significantly
outperform the state-of-the-art.
